Influences on the access to higher education: Visualization and modeling for Chilean data

### 2021-10-09 Paper_Higher_Education.Rmd
Add files via upload

Fig_5 = ggplot(final, aes(x=AGNO_EGRESO, y=Tasa, group=factor(COD_DEPE2))) +
  geom_line(linetype = "3313")+
  geom_point(aes(shape=factor(COD_DEPE2)), size=4)+ 
  labs(x="Admission Process", y="Enrolment Rate", shape="Dependence") +
  coord_cartesian(xlim = c(2008,2020.2), ylim = c(0,90))+ scale_x_continuous(breaks = c(2007:2020)) +
  scale_y_continuous(breaks = seq(0,90,10), sec.axis = dup_axis()) +
  theme_bw() +
  theme(plot.title = element_text(size = 12, face = "bold"),legend.title=element_text(size=16, angle=0),
        legend.text=element_text(size=14, angle = 0), axis.title.x = element_text(size = 18, vjust = -0.5), 
        axis.text.y = element_text(size=13, angle = 0), axis.title.y = element_text(size=18, angle=90), 
        axis.text.x = element_text(size=14, angle=90), axis.title.y.right = element_blank(), 
        legend.position = "top") + 
  geom_vline(xintercept = 2015.8, linetype="dashed") + 
  annotate(geom = "text", x = 2015.6, y = 20, label = "Gratuidad", color = "black", angle = 90) + 
  geom_vline(xintercept = 2011.8, linetype="dashed") +
  annotate(geom = "text", x = 2011.6, y = 20, label = "St.Movement", color = "black", angle = 90) + 
  geom_vline(xintercept = 2009.8, linetype="dashed") + 
  annotate(geom = "text", x = 2009.6, y = 20, label = "LGE", color = "black", angle = 90) + 
  geom_vline(xintercept = 2006.8) + 
  geom_vline(xintercept = 2019.8, linetype="dashed") + 
  annotate(geom = "text", x = 2019.6, y = 20, label = "Soc.Outbreak", color = "black", angle = 90) + 
  geom_text(aes(label = Porc), vjust= -0.9, hjust = 0, size = 4, color="black", check_overlap = TRUE, nudge_y = 0.5) +
    scale_shape_manual(values = c('Public'=15, 'Semi-Private'=17, 'Private'=16))

@@

Fig_2 = ggplot(final, aes(x=AGNO_EGRESO, y=Total_Egresados, group=factor(COD_DEPE2))) +
  geom_line(linetype = "3313")+
  geom_point(aes(shape=factor(COD_DEPE2)), size=4)+ 
  labs(x="Admission Process", y="Graduates", shape="Dependence") +
  coord_cartesian(xlim = c(2008,2020.2), ylim = c(0,100000)) +
  scale_x_continuous(breaks = c(2007:2020)) + 
  scale_y_continuous(breaks = seq(0,100000,20000), sec.axis = dup_axis()) + 
  theme_bw() +
  theme(axis.title.y.right = element_blank(),plot.title = element_text(size = 12, face = "bold"),
        legend.title=element_text(size=16, angle=0),legend.text=element_text(size=14, angle = 0),
        axis.title.x = element_text(size = 18, vjust=-0.5),   axis.text.y = element_text(size=15, angle = 0),
        axis.title.y = element_text(size=18, angle=90), axis.text.x = element_text(size=14, angle=90),
        legend.position = "top") +
  geom_vline(xintercept = 2015.8, linetype="dashed") + 
  annotate(geom = "text", x = 2015.6, y = 40000, label = "Gratuidad", color = "black", angle = 90) + 
  geom_vline(xintercept = 2011.8, linetype="dashed") + 
  annotate(geom = "text", x = 2011.6, y = 40000, label = "St.Movement", color = "black", angle = 90) + 
  geom_vline(xintercept = 2009.8, linetype="dashed") + 
  annotate(geom = "text", x = 2009.6, y = 40000, label = "LGE", color = "black", angle = 90) + 
  geom_vline(xintercept = 2006.8, linetype="dashed") + 
  geom_vline(xintercept = 2019.8, linetype="dashed") + 
  annotate(geom = "text", x = 2019.6, y = 40000, label = "Soc.Outbreak", color = "black", angle = 90) + 
  geom_text(aes(label = Porc), vjust= -0.9, hjust = 0, size = 4, color="black", check_overlap = TRUE, nudge_y = 0.5) +
  scale_shape_manual(values = c('Public'=15, 'Semi-Private'=17, 'Private'=16))

>>>>

Fig_5 = ggplot(final, aes(x=AGNO_EGRESO, y=Tasa, group=factor(COD_DEPE2))) +
  geom_line(linetype = "3313")+
  geom_point(aes(shape=factor(COD_DEPE2)), size=4)+ 
  labs(x="Admission Process", y="Enrolment Rate", shape="Dependence") +
  coord_cartesian(xlim = c(2008,2020.2), ylim = c(0,90))+ scale_x_continuous(breaks = c(2007:2020)) +
  scale_y_continuous(breaks = seq(0,90,10), sec.axis = dup_axis()) +
  theme_bw() +
  theme(plot.title = element_text(size = 12, face = "bold"),legend.title=element_text(size=16, angle=0),
        legend.text=element_text(size=14, angle = 0), axis.title.x = element_text(size = 18, vjust = -0.5), 
        axis.text.y = element_text(size=13, angle = 0), axis.title.y = element_text(size=18, angle=90), 
        axis.text.x = element_text(size=14, angle=90), axis.title.y.right = element_blank(), 
        legend.position = "top") + 
  geom_vline(xintercept = 2015.8, linetype="dashed") + 
  annotate(geom = "text", x = 2015.6, y = 15, label = "Tuition-Free Higher Education", size = 3, color = "black", angle = 90) + 
  geom_vline(xintercept = 2011.8, linetype="dashed") +
  annotate(geom = "text", x = 2011.6, y = 15, label = "Student Movement", size = 3, color = "black", angle = 90) + 
  geom_vline(xintercept = 2009.8, linetype="dashed") + 
  annotate(geom = "text", x = 2009.6, y = 15, label = "General Education Law", size = 3, color = "black", angle = 90) + 
  geom_vline(xintercept = 2006.8) + 
  geom_vline(xintercept = 2019.8, linetype="dashed") + 
  annotate(geom = "text", x = 2019.6, y = 15, label = "Social Outbreak", size = 3, color = "black", angle = 90) + 
  geom_text(aes(label = Porc), vjust= -0.9, hjust = 0, size = 3, color="black", check_overlap = TRUE, nudge_y = 0.5) +
    scale_shape_manual(values = c('Public'=15, 'Semi-Private'=17, 'Private'=16))

@@

Fig_2 = ggplot(final, aes(x=AGNO_EGRESO, y=Total_Egresados, group=factor(COD_DEPE2))) +
  geom_line(linetype = "3313")+
  geom_point(aes(shape=factor(COD_DEPE2)), size=4)+ 
  labs(x="Admission Process", y="Graduates", shape="Dependence") +
  coord_cartesian(xlim = c(2008,2020.2), ylim = c(0,100000)) +
  scale_x_continuous(breaks = c(2007:2020)) + 
  scale_y_continuous(breaks = seq(0,100000,20000), sec.axis = dup_axis()) + 
  theme_bw() +
  theme(axis.title.y.right = element_blank(),plot.title = element_text(size = 12, face = "bold"),
        legend.title=element_text(size=16, angle=0),legend.text=element_text(size=14, angle = 0),
        axis.title.x = element_text(size = 18, vjust=-0.5),   axis.text.y = element_text(size=15, angle = 0),
        axis.title.y = element_text(size=18, angle=90), axis.text.x = element_text(size=14, angle=90),
        legend.position = "top") +
  geom_vline(xintercept = 2015.8, linetype="dashed") + 
  annotate(geom = "text", x = 2015.6, y = 42000, size = 3, label = "Tuition-Free Higher Education", color = "black", angle = 90) + 
  geom_vline(xintercept = 2011.8, linetype="dashed") + 
  annotate(geom = "text", x = 2011.6, y = 42000, size = 3, label = "Student Movement", color = "black", angle = 90) + 
  geom_vline(xintercept = 2009.8, linetype="dashed") + 
  annotate(geom = "text", x = 2009.6, y = 42000, size = 3, label = "General Education Law", color = "black", angle = 90) + 
  geom_vline(xintercept = 2006.8, linetype="dashed") + 
  geom_vline(xintercept = 2019.8, linetype="dashed") + 
  annotate(geom = "text", x = 2019.6, y = 42000, size = 3, label = "Social Outbreak", color = "black", angle = 90) + 
  geom_text(aes(label = Porc), vjust= -0.9, hjust = 0, size = 4, color="black", check_overlap = TRUE, nudge_y = 0.5) +
  scale_shape_manual(values = c('Public'=15, 'Semi-Private'=17, 'Private'=16))
